\textbf{Traffic Analysis} \\ {\Large\itshape A write-up}

### 2019-03-12 paper.tex
Update paper.tex
just updating name spelling
Add files via upload

\author{\textbf{Matthew Doherty \& Daniel Delharpe} \\ \textit{Rhodes University}} % Author and institution

@@

\section{Introduction}

@@

This analysis examines events that took place on a South African network on the 2017-03-20 and 2017-03-22. We will make the argument, based purely on captured network traffic, that a host was compromised with a ransomware variant known as Maktub.

The three graphs depict packets per 10 seconds for traffic for a full network capture over the period, followed by traffic generated on the 20th and 22nd. The traffic was divided in this way to logically separate the behavior associated with each time sequence. The story of the infected host is encapsulated on the first day whereas the second day exhibits indirect behavior of the infected host as the machine has been taken offline.

@@

Legitmate windows update from Ikai CDN 
DNS for onion domain singapoor 
DNS for cryptostorm to establish VPN Germany
Get Windows-CryptoAPI from comodoca 
China DNS req  for 1.83.255.178

@@

On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence. A mail with an attachment, potentially a msword document is fetched after a "503 Backend fetch failed". The destination IP is associated with a onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes before reaching the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those most vulnerable but also those who exploit it for profit. The ".link" allows for for convenience at the expense of \cite{onionlink}. This allowed the target system to visit a TOR hidden service hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of an malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}.

@@

Following execution of the payload we can infer that the DNS quieries were made in order to resolve another .onion domain.

@@

Next we see a query for the domain cyrptostorm.is. Cryptostorm is a German based VPN service that markets itself as for the "truly paranoid" \cite{cryptostorm}. The malware then follows to make HTTP get requests with encoded URLs to a Beijing IP. This could possibly be the keys generated for the encryption based on the user agent of Mircrosoft-CryptoAPI/6.1, Microsoft's Cyrptographic Application programming interface. After this phase an TLS connection is established with the Cryptostorm using openVPN. This takes place as the user casually visits googlecode.com and stripe.com.

>>>>

\author{\textbf{Matthew Doherty \& Daniel de la Harpe} \\ \textit{Rhodes University}} % Author and institution

@@

\section{Introduction}
This analysis examines events that took place on a South African network on the 2017-03-20 and 2017-03-22. We will make the argument, based purely on captured network traffic, that a host was compromised with a ransomware variant known as Maktub. Ransomware is the term used to describe malicious software that either encrypts data (thus denying access), or threatens to leak data. The attacker will offer to stop the attack if payment is received thus the name ransomware. Maktub is of the encryption variant and is usually delivered via an email attachment, which appears legitimate but performs its malicious activity in the background.

@@

The three graphs depict packets per 10 seconds for a full network capture over the period, followed by traffic generated on the 20th and 22nd. The traffic was divided in this way to logically separate the behavior associated with each time sequence. The story of the infected host is encapsulated on the first day, whereas the second day exhibits indirect behavior of the infected host as the machine has been taken offline.

@@

Legitmate windows update from Ikai CDN 
DNS for onion domain Singapore 
DNS for cryptostorm to establish VPN Germany
Get Windows-CryptoAPI from comodoca 
China DNS req  for 1.83.255.178

@@

On the 2017-03-20 our host (10.0.0.5) seems to be engaged in routine Windows updates from IPs associated with Microsoft and Akamai (A legitimate CDN, content distribution network). The first signs of anomalous activity commence. A mail with an attachment, potentially a msword document is fetched after a "503 Backend fetch failed". The destination IP is associated with a onion domain (Host: 45jngpxc4cgsxqxc.onion.link). The .onion domain refers to TOR hidden services which require the TOR browser to interpret the protocol and connect to the site. TOR is a privacy oriented protocol which aims to obscure the origin of the sender, by encapsulating a packet in three layers of encryption before routing the packet through three intermediaries nodes on the way to the server. The protocol serves a valuable role to actors of differing motivation. The protocol is not only used by activists and those most vulnerable but also those who exploit it for profit. The ".link" allows for for convenience at the expense of \cite{onionlink}. This allowed the target system to visit a TOR hidden service hosted by our attackers. The onion link confirms our suspicions as it is associated with a malware analysis of an malicious windows executable inserted inside a benign looking update policy word document \cite{hybrid}.

@@

Following execution of the payload we can infer that the DNS queries were made in order to resolve another .onion domain.

@@

Next we see a query for the domain cyrptostorm.is. Cryptostorm is a German based VPN service that markets itself as for the "truly paranoid" \cite{cryptostorm}. The malware then follows to make HTTP get requests with encoded URLs to a Beijing IP. This could possibly be the keys generated for the encryption based on the user agent of Mircrosoft-CryptoAPI/6.1, Microsoft's Cyrptographic Application programming interface. After this phase a TLS connection is established with Cryptostorm using openVPN. This takes place as the user casually visits googlecode.com and stripe.com.
